### 2020-07-18 paper.tex
add to related work

The involutive MCMC construction encompasses many existing classes of MCMC kernels, some of which explicitly make use of bijective or involutive deterministic maps.
In particular, the reversible jump framework~\citep{green1995reversible,hastie2012model} employs a family of continuously differentiable bijections between the Euclidean parameter spaces of different models.
\citet{tierney1998note} described a family of deterministic proposals based on a deterministic involution that is equivalent to involutive MCMC but without the auxiliary proposal distribution.
More recently,~\citet{spanbauer2020deep} defined a class of deep generative model based on differentiable involutions and trained these models to serve as efficient proposal distributions on continuous state spaces; the resulting algorithm is an instance of the construction presented in this paper.
%Gen~\citet{cusumano2019gen}
%Gen's involution MCMC construct~\citet{gen-inv-mcmc}
%Reversible jump MCMC~\citet{green1995reversible}
%^Using probabilistic programs as proposals~\citet{cusumano2018using}
%Reversible jump probabilistic programming~\citet{roberts2019reversible}

>>>>

The involutive MCMC construction encompasses many existing classes of MCMC kernels, some of which explicitly make use of bijective or involutive deterministic maps.
In particular, the reversible jump framework~\citep{green1995reversible,hastie2012model} employs a family of continuously differentiable bijections between the Euclidean parameter spaces of different models.
\citet{tierney1998note} described a family of deterministic proposals based on a deterministic involution that is equivalent to involutive MCMC but without the auxiliary proposal distribution.
More recently,~\citet{spanbauer2020deep} defined a class of deep generative model based on differentiable involutions and trained these models to serve as efficient proposal distributions on continuous state spaces; the resulting algorithm is an instance of the construction presented in this paper.

In recent decades, a number of probabilistic programming systems have provided automated implementations of probabilistic inference algorithms~\citep{gilks1994language,milch2007,pfeffer200714,goodman2012church,gehr2016psi,carpenter2017stan}.
The majority of these systems have focused on the automation of one or more built-in inference algorithms, with customization limited tuning parameters of the algorithm.
The programmable inference paradigm~\citep{mansinghka2018probabilistic} to probabilistic programming instead emphasizes user control over the inference algorithm and automation of the lower-level implementation.
In particular, the Gen probabilistic programming system~\citep{cusumano2019gen} offers a high degree of user programmability by exposing an API that supports high-level user implementations of inference algorithms, instead of a set of a built-in inference engine.
One other probabilistic programming system besides Gen supports custom reversible jump samplers:
\citet{roberts2019} presents a system embedded in Haskell that can automatically generate the implementation of certain reversible jump MCMC kernels from a high-level specification, but does not handle many kernels that can be handled by our technique, including the example in Figure~\ref{fig:structure-learning}.
